Is it Better to be a Moose or a Black Bear?

### 2024-04-04 paper/paper.qmd
Updated title and subtitle of paper

---
title: "Analysis of Ontario Wildlife Harvests and Active Hunters"
subtitle: "2009-2023"
author: Samantha Barfoot
thanks: "Code and data are available at: https://github.com/SamanthaBarfoot/wildlife_hunting.git"
date: today
date-format: long
abstract: "This paper analyzes Ontario wildlife harvest counts, specifically moose and black bears, and the number fo active hunters based on region. The analysis examines harvest counts from 2012 - 2023 across northern, southeastern, and southwestern Ontario. It was found that..."
format: pdf
number-sections: true
bibliography: references.bib
---
# Introduction

>>>>

---
title: "Is it Better to be a Moose or a Black Bear?"
subtitle: "An Analysis of Ontario Wildlife Harvest and Active Hunter Rates From 2012-2023"
author: Samantha Barfoot
thanks: "Code and data are available at: https://github.com/SamanthaBarfoot/wildlife_hunting.git"
date: today
date-format: long
abstract: "This paper analyzes Ontario wildlife harvest counts, specifically moose and black bears, and the number fo active hunters based on region. The analysis examines harvest counts from 2012 - 2023 across northern, southeastern, and southwestern Ontario. It was found that..."
format: pdf
number-sections: true
bibliography: references.bib
---
# Introduction
